\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{caption}       % to allow forcing figure positions
\usepackage{float}         % to allow forcing figure posiitons
\usepackage{hyperref}		% PDF hyperreferences
\usepackage{natbib}        % to allow citet and citep citations  
\usepackage{gensymb}       % for symbols
\usepackage{wasysym}       % for special symbols like \Sun
\usepackage{multirow}      % for fancier tables
\usepackage{amsmath}       % for equation alignment

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{\LARGE Solar Eruptive Events:  \\ \large Coronal Dimming and a New CubeSat Mission}

\author{James Paul}{Mason}

\otherdegrees{B.S., University of California at Santa Cruz, 2009 \\
	          M.S., University of Colorado at Boulder, 2012}

\degree{Doctor of Philosophy}		                
	   {Ph.D., Aerospace Engineering Sciences}	

\dept{Department of}                    %  #1 {designation}
	 {Aerospace Engineering Sciences}   %  #2 {name}

\advisor{Dr.}			    %  #1 {title}
	{Thomas Woods}			%  #2 {name}

\reader{Prof. Xinlin Li}            %  2nd person to sign thesis
\readerThree{Prof. Scott Palo}	     %  3rd person to sign thesis
\readerFour{Dr. Amir Caspi}         %  4th person to sign thesis
\readerFive{Prof. Jeffrey Forbes}   %  5th person to sign thesis

\abstract{  \OnePageChapter	

	Often the abstract will be long enough to require
	more than one page, in which case the macro
	``$\backslash$OnePageChapter'' should {\it not}
	be used.

	But this one isn't, so it should.
	}

\dedication[Dedication]{
	To my late father, who inspired me from an early age to come this far. 
	}

\acknowledgements{	\OnePageChapter
First and foremost, my deepest thanks to Tom Woods. Through the projects he's introduced me to -- in solar physics, in sounding rockets, and in small satellites -- I've discovered a career path that excites me and that provides continuous opportunities to learn and contribute. Moreover, he's an excellent role model: dedicated and passionate about his work, patient with everyone without seeming to have to try, and exceptionally reliable. All of the above combined has made my time in graduate school likely to be, upon reflection long from now, one of the highlights of my life. Thank you to my committee for guidance and support, most of whom I've been fortunate to work with closely: Xinlin Li, Scott Palo, Amir Caspi, and Jeff Forbes. Finally, I couldn't have struggled through without the support of my peers, especially Allison Youngblood, whose work ethic inspires me and whom I've been extremely lucky to find. Oh, and my dog, Nessie, who requires three walks a day, has turned out to provide the periods of relaxation away from a screen that have aided in my ability to actually comprehend the work I'm doing. 
	}

\LoTisShort	% use this only for 1-page Table of Tables


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%          BEGIN DOCUMENT         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input chapter1.tex
\input chapter2.tex
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex
%\input chapter6.tex
%\input chapter7.tex
%\input chapter8.tex

%%%%%%%%%  Bibliography %%%%%%%%%
\bibliographystyle{apalike}	  % or %plain or "siam", or "alpha", etc.
\bibliography{/Users/jmason86/Dropbox/Research/Literature/library.bib}  % Bib database in from Mendeley
%\nocite{*}		% list all refs in database, cited or not

%%%%%%%%%  Appendices  %%%%%%%%%
\appendix
%\input appendixA.tex
%\input appendixB.tex
%\input appendixC.tex

\end{document}